MultiATSM package - General Guidelines

### 2025-05-11 inst/doc/Guidelines.Rmd
version 1.3.1

The previous function loads four types of datasets. The first dataset
consists of time series for zero-coupon bond yields from four emerging
markets: China, Brazil, Mexico, and Uruguay. For the purpose of the ATSM
estimation, it is important to note two requirements: *(i)* the bond
yield maturities must be consistent across all countries (although the
`DataForEstimation()` function can take different maturities as inputs,
it outputs bond yields with uniform maturities for all economies); and
*(ii)* the bond yields should be expressed in percentage terms per
annum, not in basis points. The *MultiATSM* package does not include
routines for bootstrapping zero-coupon yields from coupon bonds, so
users must handle this data manipulation themselves if needed.

@@

The second dataset focuses on the time series of risk factors. Using the
terminology of JPS (2014), this dataset includes *(i)* country-specific
**spanned factors** (commonly represented by level, slope, and curvature
-- see Section \@ref(S:SpaFac) for an intuitive explanation of these
factors) and *(ii)* a set of country-specific and global **unspanned
factors**, namely macroeconomic variables such as economic growth and 
inflation. Similar to the bond yield data, these economic indicators 
must be constructed by the user.

```{r}
data('CM_Factors')
```

The final two datasets are essential for estimating GVAR-based models.
The trade flows data, sourced from the International Monetary Fund
(IMF), presents the sum of the value of all goods imports and exports
between any two countries of the sample on a yearly basis since 1948.
All the values are free on board and are expressed in U.S. dollars.
These data are used to construct the transition matrix of the GVARs
models.

@@

The GVAR factors database casts country-specific lists of all the
factors that are used in the estimation of each country's VARX(1,1,1).
The function titled `DatabasePrep()` provides assistance to structure
the data in a similar fashion to this form. Moreover, a specific
function for computing the star risk factors is detailed in the Section
\@ref(S:SectionGVAR).

```{r}
data('CM_Factors_GVAR')
```

@@

```{r}
GVARinputs <- list(Economies = Economies, GVARFactors = FactorsGVAR, VARXtype ="constrained: Inflation")
```

@@

```{r}
data("CM_Factors_GVAR")

GVARinputs <- list(Economies = Economies, GVARFactors = FactorsGVAR, VARXtype = "unconstrained", 
                   Wgvar = W_gvar)
N <- 3

>>>>

The previous function loads three types of datasets. The first dataset
consists of time series for zero-coupon bond yields from four emerging
markets: China, Brazil, Mexico, and Uruguay. For the purpose of the ATSM
estimation, it is important to note two requirements: *(i)* the bond
yield maturities must be consistent across all countries (although the
`DataForEstimation()` and `InputsForOpt()` functions can take different 
maturities as inputs, it outputs bond yields with uniform maturities for 
all economies); and *(ii)* the bond yields should be expressed in percentage 
terms per annum, not in basis points. The *MultiATSM* package does not include 
routines for bootstrapping zero-coupon yields from coupon bonds, so users must
handle this data manipulation themselves if needed. The data can also be retrieved 
using:

@@

Bond yield data are also used to construct the country-specific **spanned** factors,
according to the terminology of JPS (2014). These factors typically correspond to 
the standard yield curve components, namely level, slope, and curvature. An intuitive 
explanation of their statistical properties is provided in Section \@ref(S:SpaFac).

The second dataset contains time series for macroeconomic risk factors — also 
referred to as **unspanned** factors, following the classification of JPS (2014). 
These include measures of economic growth and inflation for *(i)* each of the 
four countries in the sample and *(ii)* the global economy. Similar to the bond 
yield data, these economic indicators must be constructed by the user.

```{r}
data("CM_GlobalMacroFactors")
data('CM_DomMacroFactors')
```

The final dataset captures cross-country interconnectedness measures, proxied by 
bilateral trade flows, and is essential for estimating GVAR-based models. 
Specifically, the trade data—sourced from the International Monetary Fund (IMF) —
reports the annual value of total goods traded (imports plus exports)
between each pair of countries in the sample, available from 1948 onward. All the values are free on board 
and are expressed in U.S. dollars. These data are specifically used to 
construct the transition matrix of the GVAR models.

@@

@@

```{r}
data('CM_Factors_GVAR')
GVARinputs <- list(Economies = Economies, GVARFactors = FactorsGVAR, VARXtype ="constrained: Inflation")
```

@@

```{r}
data("CM_Factors_GVAR")
GVARinputs <- list(Economies = Economies, GVARFactors = FactorsGVAR, VARXtype = "unconstrained", 
                   Wgvar = W_gvar)
N <- 3
